| Early stopping in clinical PET studies: \n| how to reduce expense and exposure

### 2020-10-13 ArticleDraft/Draft.Rmd
Fixed typo in Practical recommendation box 1

$H_0: \delta = 0$

$H_1: \delta \sim Cauchy(0,0.707)$

@@

\begin{tcolorbox}[title=\textbf{Practical recommendations 1},title filled]
{In this simulation set-up we show that it is possible to stop a PET study early if there is a true underlying effect in the population, while keeping the number of false positive findings below 5\%. For a patient-control comparison, we recommend that sequential BF testing not be started until at least 12 subjects per group have been collected, adjusting the BF threshold upwards for larger values of Nmax. Importantly, these settings should only be used when the PET researcher is interested in stopping early when data shows support for H\textsubscript{1}. All BF values showing support in favour of H\textsubscript{1} (BF < 1) should not, with these settings, be interpreted as anything else but inconclusive findings.}
\end{tcolorbox}

>>>>

\newpage

$H_0: \delta = 0$
$H_1: \delta \sim Cauchy(0,0.707)$

@@

\begin{tcolorbox}[title=\textbf{Practical recommendations 1},title filled]
{In this simulation set-up we show that it is possible to stop a PET study early if there is a true underlying effect in the population, while keeping the number of false positive findings below 5\%. For a patient-control comparison, we recommend that sequential BF testing not be started until at least 12 subjects per group have been collected, adjusting the BF threshold upwards for larger values of Nmax. Importantly, these settings should only be used when the PET researcher is interested in stopping early when data shows support for H\textsubscript{1}. All BF values showing support in favour of H\textsubscript{0} (BF < 1) should not, with these settings, be interpreted as anything else but inconclusive findings.}
\end{tcolorbox}
